Study Level trends

### 2023-06-05 06_study_change.Rmd
Give up on saving table as image

```{r}
plot_table <- duration_table %>%
  filter(group %in% c("A", "B", "C", "D"))

@@

ggplot(plot_table, aes(x = duration, fill = group)) +
  geom_histogram(data = dplyr::select(plot_table, -group), fill = "grey", alpha = .5) +
  geom_histogram(colour = "black") +
  facet_wrap(~ group, labeller = group_types) +
  guides(fill = FALSE) +  # to remove the legend
  scale_fill_manual(values = group_colors) +
  theme_classic()      
```
Let's make a pretty table now
```{r, echo=FALSE}
library(kableExtra)

fun_change_table %>% 
  dplyr::select(-group) %>%
  count(rich_change, turnover, fun_change) %>%
  pivot_wider(names_from = rich_change, values_from = n) %>%
  select(fun_change, everything()) %>%
  arrange(fun_change) %>%
  mutate(`No Richness Change` = cell_spec(`No Richness Change`,
                                           color = case_when(
                                             `No Richness Change` == 12 ~ "#d9be3b",
                                             `No Richness Change` == 11 ~ "#086788",
                                             .default = "black"))) %>%
  mutate(`Richness Change` = cell_spec(`Richness Change`,
                                           color = case_when(
                                             `Richness Change` == 6 ~ "#77976e",
                                             `Richness Change` == 7 ~ "#cc8214",
                                             .default = "black"))
         ) %>%
  kable(format = "latex", col.names = c("", "", "No Richness Change", "Richness Change"), 
        booktabs = TRUE, align = "c", escape = FALSE) %>%
  kable_styling("striped") %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1:2, bold = TRUE) %>%
  collapse_rows(columns = 1, valign = "middle") %>%
  kable_as_image("figures/change_table", file_format = "jpeg", latex_header_includes = c("\\\\usepackage{booktabs}"))
```

>>>>

```{r, echo = FALSE, message = FALSE, fig.show = 'hold', fig.cap= "Break down of studies by the type of change they exhibited."}
plot_table <- duration_table %>%
  filter(group %in% c("A", "B", "C", "D"))

@@

ggplot(plot_table, aes(x = duration, fill = group)) +
  geom_histogram(data = dplyr::select(plot_table, -group), fill = "grey", alpha = .5) +
  geom_histogram(colour = "black") +
  facet_wrap(~ group, labeller = group_types) +
  ylab("count of time series") +
  guides(fill = FALSE) +  # to remove the legend
  scale_fill_manual(values = group_colors) +
  theme_classic()

library(kableExtra)

fun_change_table %>% 
  dplyr::select(-group) %>%
  count(rich_change, turnover, fun_change) %>%
  pivot_wider(names_from = rich_change, values_from = n) %>%
  select(fun_change, everything()) %>%
  arrange(fun_change) %>%
  mutate(`No Richness Change` = cell_spec(`No Richness Change`,
                                           color = case_when(
                                             `No Richness Change` == 12 ~ "#d9be3b",
                                             `No Richness Change` == 11 ~ "#086788",
                                             .default = "black"))) %>%
  mutate(`Richness Change` = cell_spec(`Richness Change`,
                                           color = case_when(
                                             `Richness Change` == 6 ~ "#77976e",
                                             `Richness Change` == 7 ~ "#cc8214",
                                             .default = "black"))
         ) %>%
  kable(format = "latex", col.names = c("", "", "No Richness Change", "Richness Change"), 
        booktabs = TRUE, align = "c", escape = FALSE) %>%
  kable_styling("striped") %>%
  row_spec(0, bold = TRUE) %>%
  column_spec(1:2, bold = TRUE) %>%
  collapse_rows(columns = 1, valign = "middle") #%>%
  #kable_as_image("figures/change_table", file_format = "jpeg", latex_header_includes = c("\\\\usepackage{booktabs}"))
```
